On the Physics of Radio Halos in Galaxy Clusters: Scaling Relations and Luminosity Functions

### 2013-09-30 paper2.tex

{\bf The presence of large-scale diffuse radio synchrotron emission in clusters
  of galaxies proves the existence of relativistic electrons and magnetic fields
  permeating the intra-cluster medium (ICM). This diffuse cluster radio emission
  can be observationally classified into two phenomena: peripheral radio relics,
  which show irregular morphology and polarized emission and appear to trace
  merger and accretion shocks, as well as radio halos (see, e.g.,
  \citealp{2012A&ARv..20...54F}).  Radio \mbox{(mini-)}halos (RHs) are
  characterized by unpolarized radio emission, are centered on clusters and
  show a regular morphology, resembling the morphology of the thermal X-ray
  emission. However, the short cooling length of synchrotron-emitting electrons
  at GHz frequencies ($\lesssim 100$~kpc) challenges theoretical model to
  explain the large-scale radio emission that extends over several Mpcs and
  calls for an efficient in-site acceleration process of electrons.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions. We thank Lawrence Rudnick
and Shea Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful 
discussions. We thank Matteo Murgia for kindly providing the radio surface brightness 
profiles of Ophiuchucs and Abell~2163 that have been recomputed with respect to the 
Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang Reich for providing the 
1.4~GHz radio map of Coma.  We also thank Miguel-Angel Perez Torres and Huub 
R{\"o}ttgering for the useful discussions.  Finally, we thank the MultiDark 
database people, in particular Adrian Partl and Kristin Riebe. 
F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of the 
program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE. 
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's Consolider-Ingenio 2010 Programme 
under grant MultiDark CSD2009-00064. C.P.{\ }gratefully acknowledges financial support
of the Klaus Tschira Foundation. The MultiDark Database used in this paper and
the web application providing online access to it were constructed as part of
the activities of the German Astrophysical Virtual Observatory as result of a
collaboration between the Leibniz-Institute for Astrophysics Potsdam (AIP) and
the Spanish MultiDark Consolider Project CSD2009-00064. The Bolshoi and
MultiDark simulations were run on the NASA's Pleiades supercomputer at the NASA
Ames Research Center.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mn2e}
%\bibliographystyle{aa}
\bibliography{bib_file}

>>>>

{\bf The presence of large-scale diffuse radio synchrotron emission in clusters
  of galaxies proves the existence of relativistic electrons and magnetic fields
  permeating the intra-cluster medium (ICM). This diffuse cluster radio emission
  can be observationally classified into two phenomena: peripheral radio relics,
  which show irregular morphology and polarized emission and appear to trace
  merger and accretion shocks, as well as radio halos (see, e.g.,
  \citealp{2012A&ARv..20...54F}).  Radio \mbox{(mini-)}halos (RHs) are
  characterized by unpolarized radio emission, are centered on clusters and
  show a regular morphology, resembling the morphology of the thermal X-ray
  emission. However, the short cooling length of synchrotron-emitting electrons
  at GHz frequencies ($\lesssim 100$~kpc) challenges theoretical models to
  explain the large-scale radio emission that extends over several Mpcs and
  calls for an efficient in-site acceleration process of electrons.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
We thank Anders Pinzke for many useful discussions and Lawrence Rudnick and Shea
Brown for a reanalysis of their 352~MHz radio map of Coma, and for useful
discussions. We thank Matteo Murgia for kindly providing the radio surface
brightness profiles of Ophiuchucs and Abell~2163 that have been recomputed with
respect to the Reiprich \& B\"{o}ringher (2002) cluster positions, and Wolfgang
Reich for providing the 1.4~GHz radio map of Coma.  We also thank Miguel-Angel
Perez Torres and Huub R{\"o}ttgering for the useful discussions.  Finally, we
thank the MultiDark database people, in particular Adrian Partl and Kristin
Riebe.  F.Z.{\ }acknowledges the CSIC financial support as a JAE-Predoc grant of
the program ``Junta para la Ampliaci\'on de Estudios'' co-financed by the FSE.
F.Z.{\ }acknowledges the hospitality of the Leiden Observatory during his stay.
F.Z.{\ }and F.P.{\ } thank the support of the Spanish MICINN's
Consolider-Ingenio 2010 Programme under grant MultiDark CSD2009-00064. C.P.{\
}gratefully acknowledges financial support of the Klaus Tschira Foundation. The
MultiDark Database used in this paper and the web application providing online
access to it were constructed as part of the activities of the German
Astrophysical Virtual Observatory as result of a collaboration between the
Leibniz-Institute for Astrophysics Potsdam (AIP) and the Spanish MultiDark
Consolider Project CSD2009-00064. The Bolshoi and MultiDark simulations were run
on the NASA's Pleiades supercomputer at the NASA Ames Research Center.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{mn2e}
\bibliography{bib_file}
